---
title: "Relatedness Between Murray Cod Larvae 2011-2013 Pipeline - Simulation Component"
author: "Alan Couch"
date: "`r format(Sys.time(), '%a %b %d %X %Y')`"
output: html_document
---
```{r, "Project_Template_and_Knitr", echo=FALSE, warning=FALSE}
#The following 2 and 4 lines are needed if knitr is to work with ProjectTemplate.
require(knitr)
if (basename(getwd()) == "src") setwd("..") #needed to get knitr to work with project template
library('ProjectTemplate') #All projectTemplates need this up front
load.project() #All projectTemplates need this up front
```

```{r "Set_Global_Options", echo=FALSE, warning=FALSE}
options(width=200)
opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
knitr::opts_chunk$set(fig.width=15, fig.height=15,fig.path="graphs/") #Make Figures larger and save them
```

```{r}
a<-suppressPackageStartupMessages({
library(related)
})

ptm <- proc.time()
```
This is the second in the pipeline. This does a simulation of known siblings to estimate cutoffs between full sibling (FS) and half sibling pairs (HS) and unrelated (UR).

We also compare the estimators and plot densities so cutoffs can be chosen.

We calculate these for each year and the same is finally calculated for all three years combined.

#Read external code Chunks
```{r echo=FALSE}
read_chunk('runRelated02sim.R')
```

```{r echo=FALSE}
read_chunk('compareRelatedestimators.R')
```

# 2011 Larval Relatedness Simulation
```{r "Simulation Relationships in 2011 Larvae"}
main<-"2011 Larval snps"
```

```{r Larvae2011, echo=FALSE}
<<simulation>>
```

```{r Larvae2011compareEstimators, echo=FALSE}
<<compareRelEstimators>>
```
So cutoffs: 

# 2012 Larval Relatedness Simulation
```{r "Simulation Relationships in 2012 Larvae"}
main<-"2012 Larval snps"
```
```{r Larvae2012, echo=FALSE}
<<simulation>>
```
```{r Larvae2012compareEstimators, echo=FALSE}
<<compareRelEstimators>>
```
So cutoffs:

# 2013 Larval Relatedness Simulation
```{r "Simulation Relationships in 2013 Larvae"}
main<-"2013 Larval snps"
```

```{r "Larvae2013", echo=FALSE}
<<simulation>>
```
```{r Larvae2013compareEstimators, echo=FALSE}
<<compareRelEstimators>>
```
So cutoffs:

# 2011-2013 Larval Relatedness Simulation
```{r "Simulation Relationships in 3 years Larvae"}
main<-"3 Years Larval snps"
```

```{r "LarvaeAllYears", echo=FALSE}
<<simulation>>
```
```{r LarvaeAllYearscompareEstimators, echo=FALSE}
<<compareRelEstimators>>
```
So cutoffs

# Include Chunks and Session Information
```{r "Include_Chunk_Labels_and_Session Information"}
all_labels()
proc.time()-ptm
#Session Information
sessionInfo()
```