---
title: "Relatedness Within and Between Years"
author: "Alan Couch"
date: "`r format(Sys.time(), '%a %b %d %X %Y')`"
output: html_document
---
```{r, "Project_Template_and_Knitr", echo=FALSE, warning=FALSE}
#The following 2 and 4 lines are needed if knitr is to work with ProjectTemplate.
require(knitr)
if (basename(getwd()) == "src") setwd("..") #needed to get knitr to work with project template
library('ProjectTemplate') #All projectTemplates need this up front
load.project() #All projectTemplates need this up front
```

```{r "Set_Global_Options", echo=FALSE, warning=FALSE}
options(width=200)
opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)

knitr::opts_chunk$set(fig.width=15, fig.height=15,fig.path="graphs/") #Make Figures larger and save them
```

```{r echo=FALSE}
a<-suppressPackageStartupMessages({
library(plyr)
library(dplyr)
library(digest)
library(igraph)
library(ggplot2)
library(data.table)
library(related)
})

ptm <- proc.time()
```

```{r echo=FALSE}
read_chunk('runRelated.R')
read_chunk('createNet.R')
```

Because the genetic diversity is low, and there is likely inbreeding among the extant population, the inbreeding mode for 'related' is set to on. This in turn means the maximum likliehood estimators must be used. This makes calculations much slower, so estimators are not compared for combinations of larvae/adults or years.

# Two of Each of the Three Years

# 2011 and 2012 Larval Relatedness
```{r "Sibling Relationships in 2011 and 2012 Larvae"}
#read file in
df<-eltwlarvalPeeliSnps; main<-"2011 and 2012 Larval snps"
df<-df[-c(1:4),]
```

```{r Larvae2011and2012, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<related>>
```
So there are `r input$nloci` loci being analysed. These are the first loci in the file ATM.

There are `r mean(input$nalleles)` alleles for each of these loci.

There are `r input$ninds` individual fish in this set.
From the simulations of 'known' relationships we can choose cut off values for identifying relationships and colouring them in the plots. In this case FS or PO above 0.4; HS 0.1-0.4; unrelated fish have a relatedness value below 0.15.

```{r Larvae2011and2012Net, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<createNet>>
```

## Refine set and Plot relationships
```{r}
#Limit to full siblings - this also makes it more sparse.
net.FS <- delete_edges(net, E(net)[weight<0.4])
l <- layout_with_fr(net.FS)

V(net.FS)$color=V(net.FS)$YearOnly #assign the "YearOnly" attribute as the vertex color
V(net.FS)$color=gsub("2011","indianred",V(net.FS)$color) #2011 will be red
V(net.FS)$color=gsub("2012","lightgoldenrod1",V(net.FS)$color) #2012 will be blue
V(net.FS)$color=gsub("2013","lightgreen",V(net.FS)$color) #2013 will be blue

E(net.FS)$weight<-E(net.FS)$weight*5

plot(net.FS, edge.arrow.size=0, edge.curved=0.2, vertex.size=5, vertex.color=V(net.FS)$color,vertex.frame.color="#555555",vertex.label=V(net)$name, vertex.label.color="black",vertex.label.cex=.7,edge.width=E(net.FS)$weight,layout=l)
#removed main=main;added edge.width=E(net.FS)$weight
title(main,cex.main=3)
legend(x=-1.5, y=-1.1, c("2011","2012", "2013"), pch=21,col="#777777", cex=.8, bty="n", ncol=1)
```

# 2011 and 2013 Larval Relatedness
```{r "Sibling Relationships in 2011 and 2013 Larvae"}
#read file in
df<-elthlarvalPeeliSnps; main<-"2011 and 2013 Larval snps"
df<-df[-c(1:4),]
```

```{r Larvae2011and2013, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<related>>
```
So there are `r input$nloci` loci being analysed. These are the first loci in the file ATM.

There are `r mean(input$nalleles)` alleles for each of these loci.

There are `r input$ninds` individual fish in this set.

From the simulations of 'known' relationships we can choose cut off values for identifying relationships and colouring them in the plots. In this case FS or PO above 0.4; HS 0.1-0.4; unrelated fish have a relatedness value below 0.15.

```{r Larvae2011and2013Net, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<createNet>>
```

## Refine Set and Plot relationships
```{r}
#Limit to full siblings - this also makes it more sparse.
net.FS <- delete_edges(net, E(net)[weight<0.4])
l <- layout_with_fr(net.FS)

V(net.FS)$color=V(net.FS)$YearOnly #assign the "YearOnly" attribute as the vertex color
V(net.FS)$color=gsub("2011","indianred",V(net.FS)$color) #2011 will be red
V(net.FS)$color=gsub("2012","lightgoldenrod1",V(net.FS)$color) #2012 will be blue
V(net.FS)$color=gsub("2013","lightgreen",V(net.FS)$color) #2013 will be blue

plot(net.FS, edge.arrow.size=0, edge.curved=0.2, vertex.size=5, vertex.color=V(net.FS)$color,vertex.frame.color="#555555",vertex.label=V(net)$name, vertex.label.color="black",vertex.label.cex=.7,layout=l, main = main)
```

# 2012 and 2013 Larval Relatedness
```{r "Sibling Relationships in 2012 and 2013 Larvae"}
#read file in
df<-twthlarvalPeeliSnps; main<-"2012 and 2013 Larval snps"
df<-df[-c(1:4),]
```
```{r Larvae2012and2013, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<related>>
```
So there are `r input$nloci` loci being analysed. These are the first loci in the file ATM.

There are `r mean(input$nalleles)` alleles for each of these loci.

There are `r input$ninds` individual fish in this set.
From the simulations of 'known' relationships we can choose cut off values for identifying relationships and colouring them in the plots. In this case FS or PO above 0.4; HS 0.1-0.4; unrelated fish have a relatedness value below 0.15.

```{r Larvae2012and2013Net, echo=TRUE,tidy=TRUE, tidy.opts=list(comment=FALSE)}
<<createNet>>
```

## Refine Set and Plot relationships
```{r}
#Limit to full siblings - this also makes it more sparse.
net.FS <- delete_edges(net, E(net)[weight<0.4])
l <- layout_with_fr(net.FS)

V(net.FS)$color=V(net.FS)$YearOnly #assign the "YearOnly" attribute as the vertex color
V(net.FS)$color=gsub("2011","indianred",V(net.FS)$color) #2011 will be red
V(net.FS)$color=gsub("2012","lightgoldenrod1",V(net.FS)$color) #2012 will be blue
V(net.FS)$color=gsub("2013","lightgreen",V(net.FS)$color) #2013 will be blue

plot(net.FS, edge.arrow.size=0, edge.curved=0.2, vertex.size=5, vertex.color=V(net.FS)$color,vertex.frame.color="#555555",vertex.label=V(net)$name, vertex.label.color="black",vertex.label.cex=.7,layout=l, main = main)
```


```{r "Include_Chunk_Labels_and_Session Information"}
all_labels()
proc.time()-ptm
#Session Information
sessionInfo()

```